The use of Synchronous and asynchronous e-learning methods and the comparison between them.\thanks{Semestrálny projekt v predmete Metódy inžinierskej práce, ak. rok 2015/16, vedenie: Ing. Jozef Sitarčík}

### 2020-10-16 Article.tex
first commit
small changes

\title{The use of Synchronous and asynchronous e-learning methods and the comparison between them.\thanks{Semestrálny projekt v predmete Metódy inžinierskej práce, ak. rok 2015/16, vedenie: Meno Priezvisko}} % meno a priezvisko vyučujúceho na cvičeniach

@@

\begin{abstract}
\ldots
\end{abstract}

\section{Abstract}

Sychronous learning happens in real-time with instantenous interaction between the participants.(Chat,Face-to-Face videocall  etc..)~\ref{nejaka}.
On the other hand Asynchronous e-learning 
is self-paced and allows individuals to gain or exchange information with each-other but not instantaneously.(e-mail
blogs, forums,websites etc..)~\ref{nejaka}.
People have been trying to prove one method's superiority over the other in order to use the better method for teaching.
Although in reality neither one is better than the other. Both methods should be used in e-learning , however
in different ways  and  in different scenarios. In this article I will talk about where and when to use asynchronous and
synchronous e-learning methods.~\ref{nejaka}. It is based on a small study done by Stefan Hrastinski.~\ref{nejaka}.
The goal of this article is to show the pros and cons of the two learning methods, and how to use them.
~\ref{nejaka}.
Dôležité súvislosti sú uvedené v častiach~\ref{dolezita} a~\ref{dolezitejsia}.
Záverečné poznámky prináša časť~\ref{zaver}.

\section{Nejaká časť} \label{nejaka}

>>>>

\title{The use of Synchronous and asynchronous e-learning methods and the comparison between them.\thanks{Semestrálny projekt v predmete Metódy inžinierskej práce, ak. rok 2015/16, vedenie: 	
Ing. Jozef Sitarčík}} % meno a priezvisko vyučujúceho na cvičeniach

@@

\begin{abstract}
\ldots
People have been trying to prove one method's superiority over the other in order to use the better method for teaching.
Although in reality neither one is better than the other. Both methods should be used in e-learning , however
in different ways  and different scenarios. In this article I will talk about where and when to use asynchronous and
synchronous e-learning methods to achieve efficient e-learning. It is based on a small study done by Stefan Hrastinski.
The goal of this article is to show the pros and cons of the two learning methods, and when and how to use them.
\end{abstract}

\section{Introduction} \label{intro}
(časť~\ref{intro:foot}).\footnote{Synchronous E-learning: Synchronous learning refers to a learning event in which a group of students are engaging in learning at the same time.}
(časť~\ref{intro:foot}).\footnote{Asynchronous E-learning: Asynchronous learning is a general term used to describe forms of education, instruction, and learning that do not occur in the same place or at the same time. It uses resources that facilitate information sharing outside the constraints of time and place among a network of people.}
Synchronous learning happens in real-time with instantaneous interaction between the participants.(Chat,Face-to-Face video call  etc..)~\ref{nejaka}.
On the other hand Asynchronous e-learning 
is self-paced and allows individuals to gain or exchange information with each-other but not instantaneously.(e-mail
blogs, forums,websites etc..)~\ref{nejaka}.
People have been trying to prove one method's superiority over the other in order to use the better method for teaching.
Although in reality neither one is better than the other. Both methods should be used in e-learning , however
in different ways  and  in different scenarios. In this article I will talk about where and when to use asynchronous and
synchronous e-learning methods.~\ref{nejaka}. It is based on a small study done by Stefan Hrastinski.~\ref{nejaka}.
The goal of this article is to show the pros and cons of the two learning methods, and how to use them.
~\ref{nejaka}.
Dôležité súvislosti sú uvedené v častiach~\ref{dolezita} a~\ref{dolezitejsia}.
Záverečné poznámky prináša časť~\ref{zaver}.

\section{Semantics} \label{nejaka}
